MSE and dynamic state variable model with sigma function

### 2018-05-14 doc/MSE_MAR_18.tex
updated tex file with spell check

Dynamic state variables have also been used to describe discarding behaviour \cite{Batsleer2015, Batsleer2013, Gillis1995}. These studies may shed light on the potential outcomes of the European fisheries management reform of 2013. That reform included using the use of the Maximum Sustainable Yield (MSY) reference points as targets for exploiting commericially important fish stocks and the gradual introduction of a landings obligation (LO) \cite{CFP2013}. Indeed, using spatial and temporal distributions of catch rates within a single year, dynamic state variable models forecasted  high costs in mixed fisheries in the short term as a result of the LO. These costs result from removing the option to adapt landings to quota by discarding parts of the catch \cite{Alzorriz2018}. This will result in fishig effort reallocation and early closures of fisheries once quota have been reached. However, the  long term benefits to fisheries that could result from improved selectivity are ignored in those studies. Ignoring the potential for improved selectivity leaves out a key element in the perceived benefit of the LO. Because the LO should provide incentives for the use of more selective gears and for fisheries to  move away from areas with high levels of unwanted catch \cite{Alzorriz2016, Alzorriz2018}, the improved selectivity should lead to higher long term catches. Achieving single species MSY while landing all commercial catches in fisheries targeting multiple species (mixed fisheries) is challenging because achieving the objective for one species may mean missing the objective for another \cite{Batsleer2013,Ulrich2017}. Forecasting whether such management will be effective depends on understanding the response of individual effort allocation to the management.

@@

maximum age                                                            & $A$                    & 4               \\
number of areas                                                       &                            & 2               \\
number of seasons                                                   & $S$                     & 6               \\
natural mortality                                                       & $M_i$                 & 0.0001     \\
Asymptotic length                                                    &  $L_{\infty_i}$   & 50            \\
Growth rate                                                              & $K_i$                 &  0.4          \\
                                                                                 & $ \alpha_i$        &  0.00005   \\
                                                                                 & $\beta_i $         &   3              \\
&               \\
\textbf{Fleet dynamics}                                           &               \\ \hline   
&  \\%& & \\

@@

\subsubsection{Size dependent pricing}
\label{sec2.2.1}
Prices of fish were assumed to be fixed over time but influenced by the body weight of the individuals in the catch, as is commonly observed \cite{Zimmermann2011, Zimmermann2013}. Following \cite{Zimmermann2011}, therelationship between fish price and body weight was modelled as:  
\begin{equation}
 p_i (a,s) = \bar{ p}_i + \gamma_i \times \frac{w_i (a,s) -\bar{w_i}}{\bar{w_i}},
\end{equation}
where $p_i (a,s) $ is the price of species $i$ at age $a$ and season $s$. The price was a linear function of the weight of inidividuals of species $i$ at age $a$ and season $s$. $\bar{p}_i$ is the price of the species at the mean weight over the age range. The mean weight over the age range is $\bar{w_i}$. $\gamma_i$ gave the price increase when individial mass was increased by $\bar{w_i}$.

\begin{figure}[!ht]
\centering
\includegraphics[width=.69\textwidth]{Figures/prices.eps} 
\caption{Lenghts and prices of the species}
\end{figure}

@@

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas and discarding patterns, the model was divided into a 'north' and 'south' area, and six fishing seasons per year. There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns is equal for the two species, and arbitrarily set to 400 per year. The species differ with respect to their nursery grounds: all individuals of species 1 are born in the southern area, while all individuals of species 2 are born in the northern area. The maximum age that any individual can reach was 4 years old

In our example, the age dependent catchability $q_i (a)$ was assumed independent of age $a$.

 A 20 \% constant migration during any season was set between areas. The migration inpopulation numbers ($M_i (a, s, im, em)$) was thus the proportion ($P (a, y, s, i, em, im)$) of the population available or vulnerable to fishing after migration occurs:

predict fish weight (W) at length (L). while assuming  ($L\infty= 20$, $k= 0.093$), with the age-weight relationship ($W= L\infty*(1-e^{-k*a})$); weight per fish was higher for the older fish.

>>>>

Dynamic state variables have also been used to describe discarding behaviour \cite{Batsleer2015, Batsleer2013, Gillis1995}. These studies may shed light on the potential outcomes of the European fisheries management reform of 2013. That reform included using the use of the Maximum Sustainable Yield (MSY) reference points as targets for exploiting commericially important fish stocks and the gradual introduction of a landings obligation (LO) \cite{CFP2013}. Indeed, using spatial and temporal distributions of catch rates within a single year, dynamic state variable models forecasted  high costs in mixed fisheries in the short term as a result of the LO. These costs result from removing the option to adapt landings to quota by discarding parts of the catch \cite{Alzorriz2018}. This will result in fishing effort reallocation and early closures of fisheries once quota have been reached. However, the  long term benefits to fisheries that could result from improved selectivity are ignored in those studies. Ignoring the potential for improved selectivity leaves out a key element in the perceived benefit of the LO. Because the LO should provide incentives for the use of more selective gears and for fisheries to  move away from areas with high levels of unwanted catch \cite{Alzorriz2016, Alzorriz2018}, the improved selectivity should lead to higher long term catches. Achieving single species MSY while landing all commercial catches in fisheries targeting multiple species (mixed fisheries) is challenging because achieving the objective for one species may mean missing the objective for another \cite{Batsleer2013,Ulrich2017}. Forecasting whether such management will be effective depends on understanding the response of individual effort allocation to the management.

@@

maximum age                                                            & $A$                    & 4               \\
number of areas                                                       &                            & 2               \\
number of seasons                                                   & $S$                     & 6               \\
natural mortality                                                       & $M_i$                 & 0.0001     \\
Asymptotic length                                                    &  $L_{\infty_i}$   & 50            \\
Growth rate                                                              & $K_i$                 &  0.4          \\
Length-weight conversion factor                             & $ \alpha_i$        &  0.00005   \\
Length-weight isomorphy factor                              & $\beta_i $         &   3              \\
&               \\
\textbf{Fleet dynamics}                                           &               \\ \hline   
&  \\%& & \\

@@

\subsubsection{Size dependent pricing}
\label{sec2.2.1}
Prices of fish were assumed to be fixed over time but influenced by the body weight of the individuals in the catch, as is commonly observed \cite{Zimmermann2011, Zimmermann2013}. Following \cite{Zimmermann2011}, therelationship between fish price and body weight was modelled as:  
\begin{equation}
 p_i (a,s) = \bar{ p}_i + \gamma_i \times \frac{w_i (a,s) -\bar{w_i}}{\bar{w_i}},
\end{equation}
where $p_i (a,s) $ is the price of species $i$ at age $a$ and season $s$. The price was a linear function of the weight of individuals of species $i$ at age $a$ and season $s$. $\bar{p}_i$ is the price of the species at the mean weight over the age range. The mean weight over the age range is $\bar{w_i}$. $\gamma_i$ gave the price increase when individual mass was increased by $\bar{w_i}$.

\begin{figure}[!ht]
\centering
\includegraphics[width=.69\textwidth]{Figures/prices.eps} 
\caption{Lengths and prices of the species}
\end{figure}

@@

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas and discarding patterns, the model was divided into a 'north' and 'south' area, and six fishing seasons per year (Table \ref{t:fishery}). There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns is equal for the two species, and arbitrarily set to 400 per year. The species differ with respect to their nursery grounds: all individuals of species 1 are born in the southern area, while all individuals of species 2 are born in the northern area. The maximum age that any individual can reach was 4 years old. During their life, individuals grew in length towards the asymptotic length, which was 50 cm. for both species. Conversion from length to weight was also equal for the two species (Table \ref{table:kysymys}).
Migration was parameterized so that a gradual diffusion occured between the two areas, euqal to 20 percent of the difference in abundance. 
 A 20 \% constant migration during any season was set between areas. The migration in population numbers ($M_i (a, s, im, em)$) was thus the proportion ($P (a, y, s, i, em, im)$) of the population available or vulnerable to fishing after migration occurs:

In the case study, age-dependent catchability links the population biomassed to the catches in the fishery, and it is thus one of the crucial parameters determing the interaction between the two. In the case study, this age-dependent catchability $q_i (a)$ was assumed independent of age $a$, and equal for the two species.

 A 20 \% constant migration during any season was set between areas. The migration in population numbers ($M_i (a, s, im, em)$) was thus the proportion ($P (a, y, s, i, em, im)$) of the population available or vulnerable to fishing after migration occurs:
